MS_CNuptake.Rmd

### 2022-07-12 MS_CNuptake.Rmd
MS CNuptake final code

# XXX what are these numbers (0.49, 18, 41, ...)?
NPP_grassland$grassland_pred_anpp <- NPP_grassland$grassland_pred_npp * 0.49
NPP_grassland$grassland_pred_lnf <- NPP_grassland$grassland_pred_anpp/18
NPP_grassland$grassland_pred_bnpp <- NPP_grassland$grassland_pred_npp - NPP_grassland$grassland_pred_anpp
NPP_grassland$grassland_pred_bnf <- NPP_grassland$grassland_pred_bnpp/41
NPP_grassland$grassland_pred_nuptake <- NPP_grassland$grassland_pred_lnf*(1-0.69)+NPP_grassland$grassland_pred_bnf

@@

# XXX what are these numbers (0.49, 1/18, 0.69, ...)?

@@

### Figure 4
```{r}
#show soil C/N effects on NUE
#aggregate
nue_all$name[nue_all$lat< -60] <- "90°S ~ 60°S"
nue_all$name[nue_all$lat >= -60 & nue_all$lat < -30] <- "60°S ~ 30°S"
nue_all$name[nue_all$lat >= -30 & nue_all$lat < 0] <- "30°S ~ 0"
nue_all$name[nue_all$lat >= 0 & nue_all$lat < 30]<- "0 ~ 30°N"
nue_all$name[nue_all$lat >= 30 & nue_all$lat < 60]<- "30°N ~ 60°N"
nue_all$name[nue_all$lat >= 60]<- "60°N ~ 90°N"

@@

#plot_grid(aa1,aa2,aa3,aa4,aa5,aa6,aa7,aa8,
#          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)'),label_size = 15)+white
#ggsave(paste("~/data/output/newphy_fig4_parallel.jpg",sep=""),width = 22, height = 10)
```

### Global maps for effect of each factor NUE (not used now)

```{r}
gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_CNrt")]),varnam = "nue_CNrt",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4", "wheat","tomato3"),
                breaks = seq(-0.05,0.05,0.01))
g1 <- gg$ggmap +labs(title = "Soil C/N")+theme_grey(base_size = 15);g2 <- gg$gglegend

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_age")]),varnam = "nue_age",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4","royalblue3","wheat","tomato3"),
                breaks = seq(-0.05,0.05,0.01))
g3 <- gg$ggmap +labs(title = "Age")+theme_grey(base_size = 15);g4 <- gg$gglegend+labs(title = ~paste("years"))

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_fAPAR")]),varnam = "nue_fAPAR",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4","royalblue3", "wheat","tomato3"),
                breaks = seq(-0.04,0.04,0.01))
g5 <- gg$ggmap +labs(title = "fAPAR")+theme_grey(base_size = 15);g6 <- gg$gglegend

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_PPFD")]),varnam = "nue_PPFD",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4", "wheat","tomato3","tomato4"),
                breaks = seq(-0.08,0.12,0.02))
g7 <- gg$ggmap +labs(title = "PPFD")+theme_grey(base_size = 15);g8 <- gg$gglegend + labs(title =~paste(mu, "mol m"^-2,"s"^-1))

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_Tg")]),varnam = "nue_Tg",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4", "wheat","tomato3"),
                breaks = seq(-0.30,0.30,0.10))
g9 <- gg$ggmap +labs(title =~paste(T[g]))+theme_grey(base_size = 15);g10 <- gg$gglegend + labs(title =~paste("\u00B0C"))

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_vpd")]),varnam = "nue_vpd",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4", "wheat","tomato3"),
                breaks = seq(-0.20,0.30,0.05))
g11 <- gg$ggmap +labs(title = "D")+theme_grey(base_size = 15);g12 <- gg$gglegend+ labs(title =~paste("kPa"))

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_vcmax25")]), varnam = "nue_vcmax25",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4", "wheat","tomato3"),
                breaks = seq(-0.2,0.2,0.04))
g15 <- gg$ggmap +labs(title =~paste(V[cmax25]))+theme_grey(base_size = 15);g16 <- gg$gglegend+ labs(title =~paste(mu, "mol m"^-2,"s"^-1))

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_LMA")]),varnam = "nue_LMA",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4", "wheat","tomato3"),
                breaks = seq(-0.05,0.05,0.01))
g17 <- gg$ggmap +labs(title = "LMA")+theme_grey(base_size = 15);g18 <- gg$gglegend+ labs(title =~paste("g ","m"^-2))

#plot_grid(g1,g2,g3,g4,g5,g6,
#          g7,g8,g9,g10,g11,g12,
#          g15,g16,g17,g18,
#          nrow=3,rel_widths = c(3/12, 1/12,3/12,1/12,3/12,1/12),
#          labels = c('(a)',' ','(b)',' ','(c)',' ',
#                     '(d)',' ','(e)',' ','(f)',' ',
#                     '(g)',' ','(h)',' '),label_size = 15)+white
#
#ggsave(paste("~/data/output/newphy_fig4_not_used.jpg",sep=""),width = 20, height = 10)

g1
g2
g3
g4
g5
g6
g7
g8
g9
g10
g11
g12
g15
g16
g17
g18
=======
plot_grid(aa1,aa2,aa3,aa4,aa5,aa6,aa7,aa8,
          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)'),label_size = 15)+white
ggsave(paste("./output/newphy_figs7.jpg",sep=""),width = 22, height = 10)
>>>>>>> dc4d6d3784f86766727dcb656a91a51ca08a6e24
```

@@

# XXX what are these numbers that you multiply here?
ISAM_fNup$myvar<- ISAM_fNup$fNup*1000*31556952

ISAM_gpp <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/ISAM_S2_gpp_ANN_mean.nc"), varnam = "gpp"))
ISAM_gpp$myvar<- ISAM_gpp$gpp*1000*31556952

ISAM_npp <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/ISAM_S2_npp_ANN_mean.nc"), varnam = "npp"))
ISAM_npp$myvar<- ISAM_npp$npp*1000*31556952

@@

ggsave(paste("./output/newphy_fortable2.jpg",sep=""), width = 23, height = 25)
```

@@

ggsave(paste("./output/newphy_fortable2.jpg",sep=""), width = 20, height = 10)
```

@@

# XXX what are these numbers (0.49, 0.51, ...)?

>>>>

# what are these numbers (0.49, 18, 41, ...)
# 0.49 as derived from anpp/tnpp ratio (fixed in grassland)
summary((lm(anpp_a~-1+tnpp_a,data=grassland_sitemean)))

#For 18 and 41 they are fixed values of leaf and root C/N, as derived from "Tian Di Grassland"
#see line 899 in https://github.com/yunkepeng/nimpl_sofun_inputs_final/blob/main/submission_newphytol/preprocessing/Forest_site_orig.R, 
#data all derived from "TianDi Grassland", but their BP, ANPP, BNPP data not used in our study
#summary(aggregate(subset(dataset6,pft=="Grassland"),by=list(subset(dataset6,pft=="Grassland")$site), FUN=mean, na.rm=TRUE)$CN_leaf_final)
#summary(aggregate(subset(dataset6,pft=="Grassland"),by=list(subset(dataset6,pft=="Grassland")$site), FUN=mean, na.rm=TRUE)$CN_root_final)

NPP_grassland$grassland_pred_anpp <- NPP_grassland$grassland_pred_npp * 0.49
NPP_grassland$grassland_pred_lnf <- NPP_grassland$grassland_pred_anpp/18
NPP_grassland$grassland_pred_bnpp <- NPP_grassland$grassland_pred_npp - NPP_grassland$grassland_pred_anpp
NPP_grassland$grassland_pred_bnf <- NPP_grassland$grassland_pred_bnpp/41
NPP_grassland$grassland_pred_nuptake <- NPP_grassland$grassland_pred_lnf*(1-0.69)+NPP_grassland$grassland_pred_bnf

@@

# what are these numbers (0.49, 1/18, 0.69, ...)
# 0.49, as explained above - are anpp/npp ratio in grassland (see line 552)
# 18, as explained above - are constant leaf C/N (see line 554)
# 0.69, as explained in above line - are constant NRE see line 442)

@@

### Figure 3
```{r}
#show soil C/N effects on NUE
#aggregate
nue_all$name[nue_all$lat< -60] <- "90°S ~ 60°S"
nue_all$name[nue_all$lat >= -60 & nue_all$lat < -30] <- "60°S ~ 30°S"
nue_all$name[nue_all$lat >= -30 & nue_all$lat < 0] <- "30°S ~ 0"
nue_all$name[nue_all$lat >= 0 & nue_all$lat < 30]<- "0 ~ 30°N"
nue_all$name[nue_all$lat >= 30 & nue_all$lat < 60]<- "30°N ~ 60°N"
nue_all$name[nue_all$lat >= 60]<- "60°N ~ 90°N"

@@

plot_grid(aa1,aa2,aa3,aa4,aa5,aa6,aa7,aa8,
          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)'),label_size = 15)+white
ggsave(paste("~/data/output/newphy_figs7.jpg",sep=""),width = 22, height = 10)
```

@@

# The values multiply here is for unit from kg/m2/month to g/m2/yr (1000 for kg to g, and 31556952 from 1/second to 1/year)
ISAM_fNup$fNup<- ISAM_fNup$fNup*1000*31556952

ISAM_gpp <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/ISAM_S2_gpp_ANN_mean.nc"), varnam = "gpp"))
ISAM_gpp$gpp<- ISAM_gpp$gpp*1000*31556952

ISAM_npp <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/ISAM_S2_npp_ANN_mean.nc"), varnam = "npp"))
ISAM_npp$npp<- ISAM_npp$npp*1000*31556952

@@

ggsave(paste("./output/newphy_fortable2a.jpg",sep=""), width = 23, height = 25)
```

@@

ggsave(paste("./output/newphy_fortable2b.jpg",sep=""), width = 20, height = 10)
```

@@

# 0.49, as explained above - are anpp/npp ratio in grassland (see line 552)
# 0.51, is 1- 0.51, for bnpp/npp ratio
